Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-01-30 paper.tex
update

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and QoS optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirement of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques. To meet users' requirement, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concerns either semantic web  service composition or QoS-aware web service composition. However, there are few works concerns both semantic matchmaking quality and QoS at the same time and achieve a more desirable tradeoff in consideration of both sides. Therefore, In this paper, proposed a general comprehensive quality model for semantic matchmaking quality and QoS. This model is also suitable to be tackled through EC algorithms, and we develop a PSO-based service composition approach with explicit support for the comprehensive model, which can generate a more desirable balance in considering semantic matchmaking quality and QoS requirement by comparing existing QoS evaluation model. We also conduct an experiment shows that our PSO-based method performs better in finding more optimised solution by comparing one existing GP-based method.

@@

The overall goal of this paper is to \textit{develop an comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach with explicit support for our proposed quality mode. We will achieve three objectives in this work as follows:

@@

 \item To evaluate our proposed approach, we conduct experiment to compare our comprehensive quality model with one widely used QoS evaluation model, we also compare an one existing GP approach with our PSO-based approach using our comprehensive model. Both comparison utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}

>>>>

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and QoS optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirement of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques. To meet users' requirement, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concerns either semantic web  service composition or QoS-aware web service composition. However, there are few works concerns both semantic matchmaking quality and QoS at the same time and achieve a more desirable tradeoff in consideration of both sides. Therefore, In this paper, proposed a general comprehensive quality model considering semantic matchmaking quality and QoS. This model is also suitable to be tackled through EC algorithms. And we develop a PSO-based service composition approach with explicit support for the comprehensive model, this method can generate a more desirable balance in considering semantic matchmaking quality and QoS requirement that is evidently supported by our experiment for comparing QoS-aware approach. We also conduct another experiment shows that our PSO-based method performs better in finding more optimised solution by comparing one existing GP-based method.

@@

The overall goal of this paper is to \textit{develop an general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach with explicit support for our proposed quality mode. We will achieve three objectives in this work as follows:

@@

 \item To evaluate our proposed approach, we conduct experiment to compare our comprehensive quality model with one widely used QoS evaluation model, we also compare an one existing GP approach with our PSO-based approach using our proposed model. Both comparison utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}
